---
title: "covid19-peru"
author: "Otto F. Proaño"
date: "11/10/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Comparing the TOTAL of people FULLY VACCINATED (2 doses) and the TOTAL confirmed DEATHS from COVID-19 by each of the 24 departments of Peru

All data for this project was obtained through the **"Plataforma Nacional de Datos Abiertos"** of Peru <https://www.datosabiertos.gob.pe/>.

For more information on data preprocessing visit the following GitHub repository <https://github.com/xxotto/covid19-peru>.

## 1. Load the packages

```{r}
library(ggplot2)
library(ggrepel)
library(dplyr)
library(broom)
library(ggpubr)
```

## 2. Import data

Read the file of "TOTAL number of people fully vaccinated (2 doses) and the TOTAL confirmed DEATHS from COVID-19 by each of the 24 departments of Peru":

```{r}
df = read.csv('../Data/DP2_TOTAL_vacunados_y_fallecidos_x_departamento.csv')
```

## 3. Linear model
```{r}
lm <- lm(tasa_mortalidad ~ vac_porcentaje, data = df)

```

## 4. Linear model
```{r}
lm_graph<-ggplot(df, aes(x=vac_porcentaje, y=tasa_mortalidad)) +
                 geom_point(color = "blue", size = 1) + 
                 geom_smooth(method="lm", col="black") +
                 ggtitle("Vaccination Rates Vs Mortality Rate", 
                         subtitle="From all deceased and fully vaccinated people (2 doses)") +
                 xlab("Percent of Fully Vaccinated") + ylab("Deaths per 100K") 
                 #geom_text_repel(aes(label = departamento), size = 2.3, 
                  #               hjust = 0.5, vjust = 0.5, 
                   #              min.segment.length = Inf)
```


```{r}
lm_graph
```





